\chapter{\noun{Threats and Inconveniences}   } \label{ti}

The way prescriptions are currently processed is vulnerable to many threats, and brings many inconveniences. The most important ones are listed below.

\section{\noun{NFZ}}

\subsection{\noun{Defraudation}}

Significant amount of money is being defrauded from NFZ because the
current system does not verify if the patient himself has bought the
medicine or the pharmacists has made a false call for the medicine
having some patient's prescription, prepared by the doctor (who is
also a part of the defraudation scheme).
Example situation: Let say that we have 2 corrupted parties in the current system - a doctor and a pharmacist. In that situation the doctor can create a fake prescription for any of his patient, then send it to the pharmacist and he - as a second party - can declare that the prescription, which is financed by NFZ, as completed.

\section{\noun{Patient}}

\subsection{\noun{Losing a prescription}}
The patient can lose the prescription and he cannot buy the medicines,
even if they are life-saving, he has to go to the doctor again and
ask for the new prescription.

\subsection{\noun{Internet shopping}}
Today we can only buy in an online pharmacy medicines which can be bought without a prescription.


\section{\noun{Pharmacy}}

\subsection{\noun{Refundation delay}}
The pharmacy has to wait long time to refund costs for the medicines
from NFZ.

\subsection{\noun{Prescriptions with mistakes}}
Prescription tend to contain mistakes which makes it useless. In this situation the patient has to go to the doctor again so it's fixed.

\section{\noun{System}}

\subsection{\noun{Prescription forgery}}
Patient can try to copy the prescription and try to buy the medicines
few times in different pharmacies.

\subsection{\noun{ Pretending that prescription was lost}}
Patient can claim that he has lost his prescription and ask the
doctor to give him another one. Then he can buy the medicines twice.
